Supplement to Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-18 supplement.tex
I added an airmass figure for comparison but my code seems to multiply the residuals because they're not the same as the time series plots.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_multi_terms.pdf}
\caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m. Error bars are shown for photon and read noise. We plot a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1). Additional terms improve the fits to the data and the $\bar{\chi^2}$.}\label{fig:model2Cosfit}
\end{centering}
\end{figure}

@@

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_multi_terms.pdf}
\caption{A zoom-in on on the time series of 2MASS J1821 for the wavelength bin 1.08~$\mu$m. Error bars are shown for photon and read noise. We plot a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1). Additional terms improve the fits to the data and the $\bar{\chi^2}$.}\label{fig:model2Cosfit}
\end{centering}
\end{figure}

@@

\clearpage{Airmass Correlation}
One thing to check is that the U shaped light curves near the telluric water bands are correlated to airmass. As I start, I used my code to look at the residuals of the single sinusoid model simultaneously with airmass.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/airmass/residuals_1p38_airmass.pdf}
\caption{Residuals of a sinusoidal fit (with hard priors to ensure fitting out the BD modulation). The magnitude of the residuals is about 5$\times$ what it should be, likely an error in the code.}\label{fig:residAirmass1p38on1821}
\end{centering}
\end{figure}
